---
title: "Housing Project"
author: "Cyrus Tadjiki"
date: "January 19th, 2022"
output: 
  html_document:
    theme: united
    highlight: tango 
    toc: yes
    toc_depth: 4
    toc_float: yes
    keep_md: true
---

<style type="text/css">

h1.title {
  font-size: 38px;
  color: Black;
  text-align: center;
}
h4.author { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: Black;
  text-align: center;
}
h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: Black;
  text-align: center;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set Up
```{r}
library(pacman)
p_load(tidyverse, magrittr, janitor, skimr, broom, MLmetrics)
```


# Cleaning Data
```{r, message=FALSE,warning=FALSE}

# Loading training dataset
df = read_csv("train.csv")
# Kaggle Method
# df = "../input/house-prices-advanced-regression-techniques//train.csv" %>% read_csv()


# Cleaning Data
df %>% dim() # Check dimension
unclean = df # Making a copy of old dataframe
df = clean_names(df) 

df = subset(df, select = -c(bsmt_qual,bsmt_cond,bsmt_exposure,
                            bsmt_fin_type1,bsmt_fin_type2,alley,
                            garage_yr_blt, lot_frontage)) # removing columns

df$pool = ifelse(df$pool_area > 1, 1, 0) # Binary Varible for having a pool

df$fireplace_good_qu =  ifelse(df$fireplace_qu == "Ex"| # Making all Average, Good, and
                               df$fireplace_qu == "Gd"| # Excellent Quality Fireplaces = 1
                               df$fireplace_qu == "TA", 1, 0) 

df$fireplace_good_qu[is.na(df$fireplace_good_qu)] = 0 # Making NAs zero
# df$fireplace_good_qu


df$fence_good =  ifelse(df$fence == "GdPrv"| df$fence == "GdWo", 1, 0)
df$fence_good[is.na(df$fence_good)] = 0 # Making NAs zero
# df$fence_good

df$mas_vnr_area[is.na(df$mas_vnr_area)] = 0 # Making NAs zero
# df$mas_vnr_area


df$heating_qc_rank = ifelse(df$heating_qc == "Ex", 5,
                     ifelse(df$heating_qc == "Gd", 4,
                     ifelse(df$heating_qc == "TA", 3,
                     ifelse(df$heating_qc == "Fa", 2,
                     ifelse(df$heating_qc == "Po", 1, 0)))))

# df$heating_qc_rank


df$central_air_ac = ifelse(df$central_air == "Y", 1, 0)
# df$central_air_ac



df$paved_drive_qu = ifelse(df$paved_drive == "Y", 2,
                    ifelse(df$paved_drive == "P", 1,0))
# df$paved_drive_qu

# names(df)[36] = "first_flr_sf"
# names(df)[37] = "second_flr_sf"
# names(df)[61] = "three_ssn_porch"

df = df %>% 
  rename(first_flr_sf = "x1st_flr_sf",
         second_flr_sf = "x2nd_flr_sf",
         three_ssn_porch = "x3ssn_porch")
```

# Viewing Data
```{r}
names(df)
skim(df) # viewing the columns
```

```{r, echo=FALSE}
# TO DO                                      
# Rename Columns 44,45,68 (these numbers are different)                          
                                      

# train_df %>% na.omit() %>% dim()
# names(df)
```


# Subsetting to Numeric Columns
```{r}
num_cols = unlist(lapply(df, is.numeric)) # Identify numeric columns  
data_num = df[ , num_cols] # Subset numeric columns of data
head(data_num)
```

# Methods
Here I ran different regressions with every numeric variable to attempt and identify what parameters are most significant for predicting housing prices.
```{r}
reg1 = lm(sale_price~.-id, data = data_num)
# tidy(reg1)
summary(reg1)


reg2 = lm(sale_price~central_air_ac, data = data_num)
# tidy(reg2)
summary(reg2)

reg3 = lm(sale_price~
          . # Everything
          -id-total_bsmt_sf-gr_liv_area # Dropping
          + poly(bsmt_unf_sf, 3) # Sig
          + poly(year_built, 3) # Sig
          + poly(bsmt_fin_sf1, 3) # Sig
          + poly(lot_area, 3), # Sig
          data = data_num)

# tidy(reg3)
summary(reg3)


reg4 = lm(sale_price~
            . # Everything
          -id-total_bsmt_sf-gr_liv_area # Dropping NA Varibles
          # Getting rid of unsig ones
          -year_remod_add-low_qual_fin_sf-bsmt_full_bath
          -bsmt_half_bath-full_bath-half_bath-garage_cars
          -open_porch_sf-enclosed_porch-three_ssn_porch
          -misc_val-mo_sold-yr_sold-pool-heating_qc_rank
          -central_air_ac-paved_drive_qu
          + poly(bsmt_unf_sf, 3) # Sig
          + poly(year_built, 3) # Sig
          + poly(bsmt_fin_sf1, 3) # Sig
          + poly(lot_area, 3), # Sig
          data = data_num)

# tidy(reg4)
summary(reg4)
```

# Loading and Cleaning Test Data Set
```{r}
## Loading Test Data
test_df = read.csv("test.csv")

# Cleaning Data
test_unclean = test_df # Making a copy of old dataframe
test_df = clean_names(test_df) 


test_df = test_df %>% 
  rename(first_flr_sf = "x1st_flr_sf",
         second_flr_sf = "x2nd_flr_sf",
         three_ssn_porch = "x3ssn_porch")

### Adding Varibles to test_df
test_df = subset(test_df, select = -c(bsmt_qual,bsmt_cond,bsmt_exposure,
                                      bsmt_fin_type1,bsmt_fin_type2,alley,
                                      garage_yr_blt, lot_frontage)) # removing columns

test_df$pool = ifelse(test_df$pool_area > 1, 1, 0) # Binary Varible for having a pool


# Making all Average, Good, and Excellent Quality Fireplaces = 1
test_df$fireplace_good_qu =  ifelse(test_df$fireplace_qu == "Ex"|
                                    test_df$fireplace_qu == "Gd"| 
                                   test_df$fireplace_qu == "TA", 1, 0) 

test_df$fireplace_good_qu[is.na(test_df$fireplace_good_qu)] = 0 # Making NAs zero
# test_df$fireplace_good_qu


test_df$fence_good =  ifelse(test_df$fence == "GdPrv"| test_df$fence == "GdWo", 1, 0)
test_df$fence_good[is.na(test_df$fence_good)] = 0 # Making NAs zero
# test_df$fence_good

test_df$mas_vnr_area[is.na(test_df$mas_vnr_area)] = 0 # Making NAs zero
# test_df$mas_vnr_area


test_df$heating_qc_rank = ifelse(test_df$heating_qc == "Ex", 5,
                          ifelse(test_df$heating_qc == "Gd", 4,
                          ifelse(test_df$heating_qc == "TA", 3,
                          ifelse(test_df$heating_qc == "Fa", 2,
                          ifelse(test_df$heating_qc == "Po", 1, 0)))))

# test_df$heating_qc_rank


test_df$central_air_ac = ifelse(test_df$central_air == "Y", 1, 0)
# test_df$central_air_ac


test_df$paved_drive_qu = ifelse(test_df$paved_drive == "Y", 2,
                         ifelse(test_df$paved_drive == "P", 1,0))
```

# Making Predictions with `predict()`
```{r, warning=FALSE}
pred = predict(object = reg1, newdata = test_df)
pred2 = predict(object = reg2, newdata = test_df)
pred3 = predict(object = reg3, newdata = test_df)
pred4 = predict(object = reg4, newdata = test_df)
```

## Removing NAs and prepping Kaggle submissions
```{r}
pred3[is.na(pred3)] = mean(pred3, na.rm = TRUE) # Making NAs mean(pred)


pred4[661] = mean(pred4, na.rm = TRUE)
pred4[1117] = mean(pred4, na.rm = TRUE)
sum(is.na(pred4))
# pred4[661]
# pred4[1117]

# Sanity Checks
# pred %>% length()
# pred2 %>% length()
# pred3 %>% length()
# pred4 %>% length()
# test_df %>% nrow()

submit_df = data.frame(
  Id = test_df$id,
  SalePrice = pred
)


submit_df2 = data.frame(
  Id = test_df$id,
  SalePrice = pred2
)

submit_df3 = data.frame(
  Id = test_df$id,
  SalePrice = pred3
)

submit_df4 = data.frame(
  Id = test_df$id,
  SalePrice = pred4
)

# View the first few lines of the dataset
head(submit_df3)  

submit_df$SalePrice[is.na(submit_df$SalePrice)] = mean(pred) # Making NAs mean(pred)
# submit_df$SalePrice

# submit_df4$SalePrice[is.na(submit_df4$SalePrice)] = mean(pred4)

# Sanity Checks
# sum(is.na(test_df$mas_vnr_area))
# sum(is.na(submit_df2$SalePrice))
# sum(is.na(submit_df3$SalePrice))
# sum(is.na(submit_df4$SalePrice))

# mean(pred2)
```

# Saving Submissions
```{r}
write_csv(x = submit_df, file = "cyrus-submit-01.csv")
write_csv(x = submit_df2, file = "cyrus-submit-01-sub2.csv")
write_csv(x = submit_df3, file = "cyrus-submit-01-sub3.csv")
write_csv(x = submit_df4, file = "cyrus-submit-01-sub4.csv")

## New Log Regs

log_reg1 = lm(sale_price~.-id, data = data_num)

# Submission Numbers
# 1108244040
# 5908414949
# 867241474
# 874791986
```

# Finding Training Performance (MSE)
```{r}

# data(cars)
# reg <- lm(log(dist) ~ log(speed), data = cars)
# MSE(y_pred = exp(reg$fitted.values), y_true = cars$dist)
# y_pred = exp(reg$fitted.values)
# y_true = cars$dist
# MSE(y_pred, y_true)


y_pred1 = reg1$fitted.values
y_true1 = df$sale_price
mse1 = MSE(y_pred1, y_true1)


y_pred2 = reg2$fitted.values
y_true2 = df$sale_price
mse2 = MSE(y_pred2, y_true2)

y_pred3 = reg3$fitted.values
y_true3 = df$sale_price
mse3 = MSE(y_pred3, y_true3)

y_pred4 = reg4$fitted.values
y_true4 = df$sale_price
mse4 = MSE(y_pred4, y_true4)
```

